Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2018-07-05 writeup/response2reviews.tex

\reply{
As we discussed in reponse to the other reviewer,
we intentionally chose simulations in this in-between spot;
they are somewhat biologically realistic 
while still retaining a clear way of obtaining the ``right'' answer 
(with regard to admixture proportions and number of discrete populations).
Additional sets of simulations will, in our opinion, make the paper too lengthy and complex;
the applications to real data we hope demonstrate the real-world utility of the method.
We have done ``sanity check'' simulations under the
multivariate-normal model itself,
but as these are far enough from biological reality (e.g., the ``frequencies'' are not between 0 and 1),
we think they'd only make the paper more confusing.
As for the migration rates -- these are given in the text \llname{ll:sim_params},
and we have added an explicit reference to this \llname{ll:sim_params_ref}.
}

### 2018-07-05 writeup/conStruct.tex
fixed typo

Even at $K=3$, ADMIXTURE invokes clusters to describe what seems to be
a continuous spatial pattern of genetic variation,
which \texttt{conStruct} describes using only two spatial layers.
The third cluster in the ADMIXTURE analysis at $K=3$ 
(shown in gold in Fig \ref{bear_admixture}b), 
shows strong spatial autocorrelation in admixture proportions, 
as would be expected if it is describing continuous spatial differentiation.
The allelic covariances plotted against distance (see Fig \ref{bear_cov_colorized})
provide more information on ADMIXTURE's lack of fit: \revpoint{1}{4}
First, covariance between Eastern bears falls off gradually rather than abruptly with distance,
indicating a residual pattern best explained by isolation by distance within layers.
Second, the covariance between bears assigned to ADMIXTURE's gold and red layers
(the furthest Northwestern and Eastern bears, respectively)
appears to be a natural extension of the decay of covariance with distance,
falling only slightly lower values than covariances 
between other widely separated pairs of Eastern sampling locations.

>>>>

Even at $K=3$, ADMIXTURE invokes clusters to describe what seems to be
a continuous spatial pattern of genetic variation,
which \texttt{conStruct} describes using only two spatial layers.
The third cluster in the ADMIXTURE analysis at $K=3$ 
(shown in gold in Fig \ref{bear_admixture}b), 
shows strong spatial autocorrelation in admixture proportions, 
as would be expected if it is describing continuous spatial differentiation.
The allelic covariances plotted against distance (see Fig \ref{bear_cov_colorized})
provide more information on ADMIXTURE's lack of fit: \revpoint{1}{4}
covariance between Eastern bears falls off gradually rather than abruptly with distance,
indicating a residual pattern best explained by isolation by distance within layers.
In addition, the covariance between bears assigned to ADMIXTURE's gold and red layers
(the furthest Northwestern and Eastern bears, respectively)
appears to be a natural extension of the decay of covariance with distance,
falling to only slightly lower values than covariances 
between other widely separated pairs of Eastern sampling locations.
